test flashr2

### 2017-09-17 analysis/flash_beta_test.Rmd
Files commited by wflow_commit.

```{r}
library(PMA)
library(softImpute)
set.seed(999)
N = 100
P = 200
dat = sim_K(K=1,N, P, SF = 0.5, SL = 0.5, signal = 1,noise = 5)
# a = rchisq(N,3)
# b = rchisq(P,1)
# data = sim_hd(N, P, SF = 0.5, SL = 0.5, signal = 1, a ,b,mu = 0)
Y = dat$Y
Y_miss = Y
Y_miss[1:50,1:100] = NA
Y_miss[51:100,101:200] = NA
```

```{r}
data = set_flash_data(Y)
g1= flash_r1(data,verbose=TRUE)
gg1 = flashr::flash(Y)
sum((as.vector(dat$L_true %*% t(dat$F_true))-as.vector(gg1$l %*% t(gg1$f)))^2)
sum((as.vector(dat$L_true %*% t(dat$F_true))-as.vector(g1$EL %*% t(g1$EF)))^2)
sum((as.vector(dat$L_true %*% t(dat$F_true))-0)^2)
```

@@

```{r}
data.miss = set_flash_data(Y_miss)
g1.miss = flash_r1(data.miss,verbose=TRUE)
```

@@

```{r}
data.miss = set_flash_data(Y_miss)
g1.miss = flash_r1(data.miss,verbose=TRUE)
gg1.miss = flashr::flash(Y_miss)
sum((as.vector(dat$L_true %*% t(dat$F_true))-as.vector(gg1.miss$l %*% t(gg1.miss$f)))^2)
sum((as.vector(dat$L_true %*% t(dat$F_true))-as.vector(g1.miss$EL %*% t(g1.miss$EF)))^2)
sum((as.vector(dat$L_true %*% t(dat$F_true))-0)^2)
```

## Session information

>>>>

```{r,message=FALSE,results=FALSE}
library(PMA)
library(softImpute)
set.seed(999)
N = 100
P = 200
dat = sim_K(K=1,N, P, SF = 0.5, SL = 0.5, signal = 1,noise = 5)
# a = rchisq(N,3)
# b = rchisq(P,1)
# data = sim_hd(N, P, SF = 0.5, SL = 0.5, signal = 1, a ,b,mu = 0)
Y = dat$Y
Y_miss = Y
Y_miss[1:50,1:100] = NA
Y_miss[51:100,101:200] = NA
```

```{r}
data = set_flash_data(Y)
g1= flash_r1(data,verbose=F)
gg1 = flashr::flash(Y,ash_para_l = list(method = "shrink"),ash_para_f = list(method = "shrink"))
sum((as.vector(dat$L_true %*% t(dat$F_true))-as.vector(gg1$l %*% t(gg1$f)))^2)
sum((as.vector(dat$L_true %*% t(dat$F_true))-as.vector(g1$EL %*% t(g1$EF)))^2)
sum((as.vector(dat$L_true %*% t(dat$F_true))-0)^2)
```

@@

```{r}
data.miss = set_flash_data(Y_miss)
g1.miss = flash_r1(data.miss,verbose=F)
```

@@

```{r}
data.miss = set_flash_data(Y_miss)
g1.miss = flash_r1(data.miss,verbose=F)
gg1.miss = flashr::flash(Y_miss,ash_para_l = list(method = "shrink"),ash_para_f = list(method = "shrink"))
sum((as.vector(dat$L_true %*% t(dat$F_true))-as.vector(gg1.miss$l %*% t(gg1.miss$f)))^2)
sum((as.vector(dat$L_true %*% t(dat$F_true))-as.vector(g1.miss$EL %*% t(g1.miss$EF)))^2)
sum((as.vector(dat$L_true %*% t(dat$F_true))-0)^2)
```

## compare versions

In this case, we set flash use `shrink` method and compare with the new version.

```{r}
sparse_level_l = seq(0.1,0.9,0.2)
sparse_level_f = seq(0.1,0.9,0.2)
signal_level = seq(1,5)
RMSE_1 = rep(NA,5*5*5)
RMSE_2 = rep(NA,5*5*5)
for(i in 1:5){
  for(j in 1:5){
    for(k in 1:5){
      set.seed(999)
      N = 100
      P = 200
      dat = sim_K(K=1,N, P, SF = sparse_level_f[i],
                  SL = sparse_level_l[j], 
                  signal = signal_level[k],
                  noise = 5)
      Y = dat$Y
      data = set_flash_data(Y)
      g1= flash_r1(data,verbose=F)
      gg1 = flashr::flash(Y,ash_para_l = list(method = "shrink"),ash_para_f = list(method = "shrink"))
      RMSE_1[25*(i-1) + 5*(j-1) + k] = 
        sqrt(mean((as.vector(dat$L_true %*% t(dat$F_true))-as.vector(gg1$l %*% t(gg1$f)))^2))/sqrt(mean((as.vector(dat$L_true %*% t(dat$F_true))-0)^2))
      RMSE_2[25*(i-1) + 5*(j-1) + k] = 
        sqrt(mean((as.vector(dat$L_true %*% t(dat$F_true))-as.vector(g1$EL %*% t(g1$EF)))^2))/sqrt(mean((as.vector(dat$L_true %*% t(dat$F_true))-0)^2))
    }
  }
}

plot(RMSE_1 - RMSE_2)
```

To check the extreme case, and I found it is because flashr doesn't output rand zero estimation where zero estimation is better.

```{r}
i = 5
j = 5
k = 1
set.seed(999)
N = 100
P = 200
dat = sim_K(K=1,N, P, SF = sparse_level_f[i],
            SL = sparse_level_l[j], 
            signal = signal_level[k],
            noise = 5)
Y = dat$Y
data = set_flash_data(Y)
g1= flash_r1(data,verbose=F)
gg1 = flashr::flash(Y,ash_para_l = list(method = "shrink"),ash_para_f = list(method = "shrink"))

  sqrt(mean((as.vector(dat$L_true %*% t(dat$F_true))-as.vector(gg1$l %*% t(gg1$f)))^2))/sqrt(mean((as.vector(dat$L_true %*% t(dat$F_true))-0)^2))

  sqrt(mean((as.vector(dat$L_true %*% t(dat$F_true))-as.vector(g1$EL %*% t(g1$EF)))^2))/sqrt(mean((as.vector(dat$L_true %*% t(dat$F_true))-0)^2))

```
## Session information
